Correlation between different emission channels from an atom inside a leaky driven cavity

### 2019-12-18 newpaper.tex
Quase listo. Leer todos con cuidado

Spontaneous emission is a phenomenon that has been studied since the
early XX century \cite{10.2307/94746, 1917PhyZ...18..121E}. One of the
main characteristics of spontaneous emission is that the exact time of
emission, as well as the direction in which the photon is emitted, is
random, which difficults its measurement. On the other hand, photons
emitted from a cavity mirror are easier to measure because we know
their direction \cite{326305, doi:10.1063/1.113345}. The randomness of
the direction in which the photons are emitted by atoms in free space
difficults photon counting experiments. To sort out this difficulty
one could think of a physical arrangement in which a two-level atom is
coupled to a driven cavity, as it is shown in Fig. \ref{asa}. In this
physical arrangement, one could try to estimate the number of
spontaneous emissions of the atom --which are emitted in modes that
are not cavity modes and therefore escape the cavity to its side-- by
measuring the photons that leak through one of the cavity mirrors. In
the case that a correlation exists between the two quantities, we can
count the number of photons that leak the cavity through its mirror,
which is easy to measure, to find information about the number of
photons emitted into the other modes (spontaneus emission), which are
difficult to measure.

@@

For an atom in free space, knowing the number of photons emitted in
some region of the space during some time does not give any
information on the number of photons emitted in other region of the
space. Nevertheless, for the case of an atom inside a cavity, before a
photon, emitted from the atom into the cavity mode, leaks the cavity,
it will interact with the atom for some time. This interaction creates
a correlation between photons that leak the cavity through its mirror
and photons that are emitted from the atom to the cavity side
(spontaneus emissions).

We use quantum trajectories theory to calculate the correlation between
different emission channels. A quantum trajectory is the description
of a continuously monitored quantum system conditioned on a particular
past history of coherent evolution and collapse
\cite{Carmichael1993Open}. These trajectories are simulated through a
stochastic process, which define the times when the collapses occur.
Each trajectory gives us the number of photon emitted in each channel.
Simulating a large number of trajectories and registering the number
of photon emissions into the two channels, we obtain its correlation.
The correlation varies with the cavity linewidth and the atom-cavity
coupling. For a very bad cavity we recover the free space result:
there is no correlation between the two channels.

This article is organized as follows: A general overview of the
theoretical model is presented in section \ref{sc:drivenjc}. In
section \ref{sc:distributions} we obtain join probability distribution
of the the number of spontaneous and cavity emissions. In section
\ref{sc:correlation} we calculate the correlation between the two
variables. Concluding remarks are given in section
\ref{sc:conclusions}
\begin{center}
\begin{figure*}\label{asa}
\begin{center}
\includegraphics[scale = 0.65]{newimagepaper.pdf}
%\includegraphics[scale = 0.45]{image_paper222.png}
\caption{A driven atom in free space (a) and inside a driven leaky
  cavity (b). We count the number of photons $m$ and $n$, emitted by
  the atom in two different directions. For the atom in free space
  there is no correlation between $m$ and $n$. For the atom inside the
  leaky cavity we find a correlation between $m$ and $n$.}
\end{center}
\end{figure*}
\end{center}

\section{Theoretical model}\label{sc:drivenjc}
We consider a system consisting of a two-level atom, coupled to a mode
of a leaky cavity. The mode is driven by a coherent field resonant
with the atomic transition and the cavity mode.
% In order to account for
% dissipation one may use a non-hermitian Hamiltonian to describe the
% system \cite{bla}. Using this description for the system will turn
% useful at the moment of using quantum trajectory theory. Such
% Hamiltonian can be separated into hermitian and non-hermitian terms.
%\begin{equation}
%H = H_s - \frac{i\hbar}{2}\sum_m C^\dagger_n C_n .
%\end{equation}
The Hamiltonian of this system, in the rotating wave approximation is
given by
\begin{equation}
H_s = H_{at} + H_{cav} + H_{atcav} + H_{lascav}, \label{mainham}  
\end{equation}
where the atom and cavity terms are, respectively
\begin{subequations}
\begin{equation}
H_{at} = \tfrac{1}{2}\hbar \omega \sigma_z,    
\end{equation}
\begin{equation}
H_{cav} = \hbar \omega  a^\dagger a,  
\end{equation}
while the coupling between atom and cavity, and cavity and coherent
field are
\begin{equation}
H_{atcav} = i\hbar g(a\sigma_+ - a^\dagger \sigma_-),    
\end{equation}
\begin{equation}
H_{lascav} = i\hbar \mathcal{E}(ae^{i\omega t} - a^\dagger e^{-i\omega t}),    
\end{equation}
\end{subequations}
where the annihilation operator $a$ of a single photon in the cavity,
and the creation operator $a^\dagger$ obey $[a, a^\dagger] = 1$. The
operators $\sigma_-, \sigma_+$ account for the atomic lowering and
raising operators, respectively, and the operator $\sigma_z$ accounts
for the population difference between the atomic levels. These
operators obey
$[\sigma_+, \sigma_-] = \sigma_z, \ [\sigma_\pm, \sigma_z] = \mp
2\sigma_\pm$. The strength of the coupling between atom and cavity
field is given by the constant
\begin{equation}
g = \sqrt{\frac{\omega d^2}{2\hbar \epsilon_0 V_Q}},
\end{equation}
where $V_Q$ is the mode volume , $d$ is the atomic dipole , and
$\epsilon_0$ is the permitivity of free space. $\mathcal{E}$ is a term
proportional to the coherent field amplitude. Dissipation is
introduced by the following non-hermitian Hamiltonian
\begin{equation} \label{nh}
H_{nh} = H_{dec} + H_{leak},
\end{equation}
where the terms corresponding to spontaneous emission of the atom and cavity losses are
\begin{subequations}
\begin{equation}
H_{dec} = - i\hbar\frac{\gamma}{2}\sigma_+\sigma_-,
\end{equation}
\begin{equation}
H_{leak} = - i\hbar\kappa a^\dagger a\, ,
\end{equation}
\end{subequations}
where $\kappa$ and $\gamma$ are the cavity loss and spontaneous decay
rate. The evolution between jumps is given by $H=H_s+H_{nh}$. This
evolution is interrumped by spontaneus emission by the atom or when a
photon leaks the cavity.

We now summarize te quantum trajectory formalism \cite{bla} that we
use to solve the system. Each quantum trajectory is simulated as
folllows. We start with a state which represents a ground state of the
atom with no photons in the cavity,
$\ket{\phi(t = 0)} = \ket{\downarrow} \times \ket{0}$, we evolve it
with the Schrödinger equation through some time $\delta t$, using the
non-hermitian Hamiltonian
\begin{equation}
H = H_s +H_{nh}\, .
\end{equation}
The evolution of the state through the schrödinger equation will be
interrupted by a quantum jump – an abrupt change on our state in which
a photoemission has ocurred. The probability for such quantum jump to
happen, during the time step $\delta t$, is given by the collapse
probability
\begin{equation} \label{probcol}
\delta p = \sum_n \delta p_n,
\end{equation}
where

@@

\ENDIF
\ELSE
\STATE $\ket{ \phi(t + \delta t)} = \frac{\ket{\phi^1 (t+ \delta t)}}{\sqrt{1-\delta p}}$
\STATE $t \ += \delta t$
\ENDIF
\ENDFOR
\RETURN  $N_{CA}$
\end{algorithmic}
\end{algorithm}
We compare the collapse probability of Eq.~\eqref{probcol} with a
random number $\epsilon$, uniformly distributed between zero and one.
In the case the condition $\delta p > \epsilon$ is fulfilled we
simulate that a quantum jump has happened, by acting with one of the
collapse operators $a$ or $\sigma_-$ and renormalizating the obtained
state. The operator that will act on the state will be given according
to the relative probabilities of Eqs.~\eqref{relprob}.
\begin{figure}[!t] 
\centering
\includegraphics[scale = 0.5]{distributioneng.pdf}
\caption{Probability distribution of spontaneous emissions for
  different number of cavity photons. Parameters $\mathcal{E}  =
  \kappa = \gamma = g = 1$, $100,000$ quantum trajectories. } \label{probdiss}
\end{figure}
If $\delta p > \epsilon$ is not fulfilled we just renormalize the
state, because using a non-hermitian Hamiltonian will have as a
consequence that the probability won't be conserved
\cite{Sakurai:1167961}. For the next step we repeat the procedure
using the resulting state for this step. One quantum trajectory of
total time $t$ is obtained after repeating the previous procedure
$t/\delta t$ steps. For each trajectory we count the number of quantum
jumps, the jumps correponding to operator $a$ reduces the number of
photons inside the cavity and corresponds to a photon that leak the
cavity. The jumps corresponding to operator $\sigma_-$ interrumps its
unitary evolution and send it back to the ground state, it corresponds
to a spontaneous emission. The procedure to register emissions in the
two different channels is summarized in algorithm. \ref{alg1}.

@@

\section{Counting photons emitted in different channels}\label{sc:distributions}
In this section we calculate the probability distribution of the
number of spontaneous emissions $n_s$, under two different conditions.
First, we study the distribution probability of $n_s$ when we consider
the set of quantum trajectories where the number of leaked photons
from the cavity is $n_c$. This simulate the physical situation where
we count the number of spontaneus photons until the moment where the
number of leaked photons from the cavity is $n_c$. It is impossible to
know in advance how long it takes to the cavity to leak $n_c$ photons,
thus the time each quantum trajectory is evolved is not fixed. Second,
we fix the time each quantum trajectory is evolved and count the
number of spontaneus emissions $n_s$, and cavity emissions $n_c$. From
the set of quantum trajectories evolved a fixed time, we calculate the
joint probability $p(n_s,n_c)$, of finding $n_s$ spontaneous emissions
and $n_c$ cavity emissions. Using $p(n_s,n_c)$ we calculate the
correlations between the two random variables. This correlation is a
measure of how much information we can obtain about $n_s$ if we know
$n_c$.

@@

In order to find the value of the cavity drive $\mathcal{E}$ as a
function of the mean value of photons inside the cavity, we solve the
Maxwell-Bloch equations. These equations give the dynamic of our
system for the variables $\expval{a}, \expval{\sigma_-}$ and
$\expval{\sigma_z}$ that correspond to the cavity field, atomic
coherence, and atomic inversion respectively \cite{Alsing_1991}. For
the case of the driven Jaynes-Cummings system, these equations are
\begin{subequations} \label{maxbloch}
\begin{equation} \label{bloch1}
\dot{z} = (g/2)v + \mathcal{E} - \kappa z,
\end{equation}
\begin{equation} \label{bloch2}
\dot{v} = gmz - (\gamma/2)v,
\end{equation}
\begin{equation} \label{bloch3}
\dot{m} = -2g(z^*v + v^*z) - \gamma(m + 2),
\end{equation}
\end{subequations} 
where we defined $z = e^{i\omega t}\expval{a}$,
$v = 2e^{i\omega t}\expval{\sigma_-}$ and $m = 2\expval{\sigma_z}$.
When the system is stable, we obtain, from
\eqref{maxbloch}, the steady state
solutions \cite{gagniuc2017markov}

@@

\subsection{Quantum trajectories with fixed number of photons leaked from the cavity}
We calculate the distribution probability of the number of spontaneous
emission when a fixed number of photons leaked the cavity. We assume
that the mean number of photons inside the cavity is $1/9$. The
results are shown in Fig.~\ref{probdiss}. As the number of leaked
photons increases, the mean number of spontaneous emissions increases.
This result is expected, because the number of leaked photons is
correlated with the time we are counting spontaneus emission photons
from a driven atom: the larger the number of leaked photons the larger
the time we measure spontaneous emitted photons, which implies a
larger mean number of emitted photons. Also, as shown in
Fig~\ref{graph}, the probability distribution is wider as the number
of leaked photons increases, this implies less accuracy guessing the
number of spontaneus emission. If we know the cavity drive, this
results does not imply that we can learn something extra about the
number of spontaneous emissions knowing the number of photons leaked
from the cavity; it is clear that when we increase the time window
where we count photons, both, the number of leaked photons and the
number of spontaneous emissions, increases.

@@

\begin{figure}[!h]  
\centering
\includegraphics[scale = 0.5]{newsigmaeng.pdf}
\caption{Average number of spontaneous emissions $\pm \sigma$ with respect to cavity emissions, under parameters $\expval{n} \approx 1$, $\gamma = 1$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}
\label{graph}
\end{figure}

\subsection{Quantum trajectories with fixed duration}
We consider the set of quantum trajectories of the same duration. This
corresponds to fixing the time we measure photons. Each set of quantum
trajectories with the same duration is labelled with its mean number
of spontaneous emitted photons $\mu$. We consider the case where we
fix the mean number of photons inside the cavity to $1$. As shown by
Eq.~(\ref{numfo}), this number depends on the drive, and cavity and
atomic parameters.

In Fig.~\ref{error2}(a) the probability distribution of spontaneous
emitted photons is shown for different mean values. As it is shown in
Fig.~\ref{error2}(b), the width of the distribution increases linearly
with the mean number of spontaneus emission. This behaviour does not
imply any correlation between the number of spontaneus emissions and
cavity emissions.

Now we focus in the case, where given a set of quantum trajectories
with fixed duration, we postselect all the trajectories where the
number of cavity emissions is a fixed number $n_c$, and plot
$p(n_s|n_c)$, the probability distribution of the number of spontaneus
emissions $n_s$, under the condition that $n_c$ cavity emissions
happened. If $p(n_s|n_c)\neq p(n_s)p(n_c)$, $n_s$ and $n_c$ are not
independent: information can be extracted about $n_s$ knowing $n_c$.
In Fig.~\ref{probdisult} (a) we show the probability distribution of
$n_s$ for the case where $n_c$.

In Fig.~\ref{probdisult} (b), where we obtain a variance almost equal
to the mean value, something which is characteristic of Poisson
distributions.

\begin{center}
\begin{figure*}[!t]
\includegraphics[scale = 0.7]{newerrorppp.pdf}
\caption{(a) Probability distributions for different mean number of
  spontaneous emissions $\mu$; (b) Calculation of variance with
  respect to the mean number of sponatenous emissions $\mu$. In both
  cases we consider $\expval{n} \approx 1$, $\gamma = 1.0$ ,
  $\kappa = g = 0.1$ and
  $\mathcal{E} = \kappa |\langle n \rangle|[1 + 2g^2/\gamma
  \kappa]$.} \label{error2}
\end{figure*}
\end{center}

\begin{center}
\begin{figure*}
\begin{center}
\includegraphics[scale = 0.7]{lastgraph1.pdf}
\caption{\small{Mean value of spontaneous emissions after post-selection, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$ and with tf = 500. (a) We consider $\kappa = $0.05 which has a correlation value around $0.1$; (b) we consider $\kappa = $1.0, which has a correlation value around $0.01$.}} \label{probdisult}
\end{center}
\end{figure*}
\end{center}

\section{Correlation between photons emitted in different channels}\label{sc:correlation}
In this section we study the correlation between the number of
spontaneus emission from the atom, $n_s$, and the number of photons
that leak the cavity, $n_c$, as a function of the cavity decay rate,
$\kappa$. We expect that when $\kappa\rightarrow\infty$ there would be
no correlation between these two random variables, since this
situation will be equivalent to the situation where there is no
cavity.

In order to have a measure of the correlation between emissions in the
two different channels, we use the Pearson Correlation Coefficient
\cite{benesty2009pearson}
\begin{equation} 
r_{n_s,n_c} = \frac{\sum\limits_{i=1}^n(n_s^{(i)} -
  \bar{n}_s)(n_c^{(i)} - \bar{n}_c)}{\sqrt{\sum\limits_{i=1}^n(n_s^{(i)}
    - \bar{n}_s)^2\sum\limits_{i=1}^n(n_c^{(i)} - \bar{n}_c)^2}}\, ,  \label{correlationc}
\end{equation}
where $n^{(i)}$ is the output $i$ of the random variable $n$.

\begin{center}
\begin{figure}[t!]
\begin{center}
\includegraphics[scale = 0.5]{million1.pdf}
\caption{\small{Calculation of correlation using a time interval, tf = 500, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{corrxy}
\end{center}  
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h!]
\begin{center}
\includegraphics[scale = 0.5]{million2.pdf}
\caption{\small{Correlation using different temporal intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g =$ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}  \label{errorzz}
\end{center}
\end{figure}
\end{center}
%kncrease or increases

@@

The results are shown in Fig. \ref{corrxy}. We see a maximum
correlation close to $0.1$ for $\kappa/\gamma\approx 0.05$ that
decreases as $\kappa$ increases. From the figure it looks like the
correlation goes to zero as $\kappa\rightarrow\infty$. With values for
$\kappa/\gamma$ lower than $0.05$, we notice that the correlations
increase stops and a decrease begins. This stop in the increase of the
correlation is due to the fact that, as we keep decreasing the cavity
linewidth the number of photons that leaks the cavity decreases
considerably. In the limit where $\kappa=0$ the two random
variables becomes independent, because the output of $n_c$ is zero
with probability one. In this case there is no correlation between the two
random variables.

In Fig. \ref{errorzz} it is shown that as we increase the temporal
interval where we count photons, we also see a small increment of the
correlation, due to the fact that more photons leaks the cavity
giving information about the system.
\fxnote{Hay que mejorar las graficas. Las variables tienen que ser
  mayores y las unidades estan mal}

>>>>

Spontaneous emission is a phenomenon that has been studied since the
early XX century \cite{10.2307/94746, 1917PhyZ...18..121E}. One of the
main characteristics of spontaneous emission is that the exact time of
emission, as well as the direction in which the photon is emitted, is
random, which difficults its measurement. On the other hand, photons
emitted from a cavity mirror are easier to measure because we know
their direction \cite{326305, doi:10.1063/1.113345}. The randomness of
the direction in which the photons are emitted by atoms in free space
difficults photon counting experiments. To sort out this difficulty
one could think of a physical arrangement in which a two-level atom is
coupled to a driven cavity, as it is shown in Fig. \ref{asa}. In this
physical arrangement, one could try to estimate the number of
spontaneous emissions of the atom --photons that are emitted in modes
that are not cavity modes and therefore escape the cavity to its
side-- by measuring the cavity emissions --photons that leak through
one of the cavity mirrors. In the case that a correlation exists
between the two quantities, we can count the number of photons that
leak the cavity through its mirror, which is easy to measure, to find
information about the number of photons emitted into the other modes
(spontaneous emission), which are difficult to measure.

@@

For an atom in free space, knowing the number of photons emitted in
some region of the space during some time does not give any
information on the number of photons emitted in other region of the
space. Nevertheless, for the case of an atom inside a cavity, before a
photon, emitted from the atom into the cavity mode, leaks the cavity,
it will interact with the atom for some time. This interaction could
create a correlation between photons that leak the cavity through its
mirror and photons that are emitted from the atom to the cavity side
(spontaneous emissions).

We use quantum trajectories to calculate the joint probability of the
number of spontaneus emissions and the number of cavity emission. A
quantum trajectory describes a continuously monitored quantum system
\cite{Carmichael1993Open}. In our case each trajectory gives the
number of photons emitted in each channel. Simulating a large number
of trajectories and registering the number of photon emissions into
the two channels, we obtain its joint probability distribution and
their correlation. The correlation varies with the cavity linewidth
and the atom-cavity coupling. For a very bad cavity we recover the
free space result: there is no correlation between the two channels.

This article is organized as follows: A general overview of the
theoretical model is presented in section \ref{sc:drivenjc}. In
section \ref{sc:distributions} we obtain the joint probability
distribution of the  number of spontaneous and cavity emissions. In
section \ref{sc:correlation} we calculate the correlation between the
two variables. Concluding remarks are given in section
\ref{sc:conclusions}
\begin{center}
\begin{figure*}\label{asa}
\begin{center}
\includegraphics[scale = 0.65]{newimagepaper.pdf}
%\includegraphics[scale = 0.45]{image_paper222.png}
\caption{A driven atom in free space (a) and inside a driven leaky
  cavity (b). We count the number of photons $m$ and $n$, emitted by
  the atom in two different directions. For the atom in free space
  there is no correlation between $m$ and $n$. For the atom inside the
  leaky cavity we find a correlation between $m$ and $n$.}
\end{center}
\end{figure*}
\end{center}

\section{Theoretical model}\label{sc:drivenjc}
We consider a system consisting of a two-level atom, coupled to a mode
of a leaky cavity. The mode is driven by a coherent field resonant
with the atomic transition and the cavity mode.
% In order to account for
% dissipation one may use a non-hermitian Hamiltonian to describe the
% system \cite{bla}. Using this description for the system will turn
% useful at the moment of using quantum trajectory theory. Such
% Hamiltonian can be separated into hermitian and non-hermitian terms.
%\begin{equation}
%H = H_s - \frac{i\hbar}{2}\sum_m C^\dagger_n C_n .
%\end{equation}
The Hamiltonian of this system, in the rotating wave approximation is
given by
\begin{equation}
H_s = H_{at} + H_{cav} + H_{atcav} + H_{lascav}, \label{mainham}  
\end{equation}
where the atom and cavity terms are, respectively
\begin{subequations}
\begin{equation}
H_{at} = \tfrac{1}{2}\hbar \omega \sigma_z,    
\end{equation}
\begin{equation}
H_{cav} = \hbar \omega  a^\dagger a,  
\end{equation}
while the coupling between atom and cavity, and cavity and coherent
field are
\begin{equation}
H_{atcav} = i\hbar g(a\sigma_+ - a^\dagger \sigma_-),    
\end{equation}
\begin{equation}
H_{lascav} = i\hbar \mathcal{E}(ae^{i\omega t} - a^\dagger e^{-i\omega t}),    
\end{equation}
\end{subequations}
where the annihilation operator $a$ of a single photon in the cavity,
and the creation operator $a^\dagger$ obey $[a, a^\dagger] = 1$. The
operators $\sigma_-, \sigma_+$ account for the atomic lowering and
raising operators, respectively, and the operator $\sigma_z$ accounts
for the population difference between the atomic levels. These
operators obey
$[\sigma_+, \sigma_-] = \sigma_z, \ [\sigma_\pm, \sigma_z] = \mp
2\sigma_\pm$. The strength of the coupling between atom and cavity
field is given by the constant
\begin{equation}
g = \sqrt{\frac{\omega d^2}{2\hbar \epsilon_0 V_Q}},
\end{equation}
where $V_Q$ is the mode volume, $d$ is the atomic dipole, and
$\epsilon_0$ is the permittivity of free space. $\mathcal{E}$ is a term
proportional to the coherent field amplitude. Dissipation is
introduced by the following non-hermitian Hamiltonian
\begin{equation} \label{nh}
H_{nh} = H_{dec} + H_{leak},
\end{equation}
where the terms corresponding to spontaneous emission of the atom and cavity losses are
\begin{subequations}
\begin{equation}
H_{dec} = - i\hbar\frac{\gamma}{2}\sigma_+\sigma_-,
\end{equation}
\begin{equation}
H_{leak} = - i\hbar\kappa a^\dagger a\, ,
\end{equation}
\end{subequations}
where $\kappa$ and $\gamma$ are the cavity loss and spontaneous decay
rate. The evolution between jumps is given by $H=H_s+H_{nh}$. This
evolution is interrupted by spontaneous emission by the atom or when a
photon leaks the cavity.

We now summarize the quantum trajectory formalism \cite{bla} that we
use to solve the system. Each quantum trajectory is simulated as
follows. We start with a state which represents a ground state of the
atom with no photons in the cavity,
$\ket{\phi(t = 0)} = \ket{\downarrow} \times \ket{0}$, we evolve it
with the Schrödinger equation through some time $\delta t$, using the
non-hermitian Hamiltonian
\begin{equation}
H = H_s +H_{nh}\, .
\end{equation}
The evolution of the state through the Schrodinger equation will be
interrupted by a quantum jump – an abrupt change on our state in which
a photoemission has occurred. The probability for such quantum jump to
happen, during the time step $\delta t$, is given by the collapse
probability
\begin{equation} \label{probcol}
\delta p = \sum_n \delta p_n,
\end{equation}
where

@@

\ENDIF
\ELSE
\STATE $\ket{ \phi(t + \delta t)} = \frac{\ket{\phi^1 (t+ \delta t)}}{\sqrt{1-\delta p}}$
\STATE $t \ += \delta t$
\ENDIF
\ENDFOR
\RETURN  $N_{CA}$
\end{algorithmic}
\end{algorithm}
We compare the collapse probability of Eq.~\eqref{probcol} with a
random number $\epsilon$, uniformly distributed between zero and one.
In the case the condition $\delta p > \epsilon$ is fulfilled we
simulate that a quantum jump has happened, by acting with one of the
collapse operators $a$ or $\sigma_-$ and renormalizating the obtained
state. The operator that will act on the state will be given according
to the relative probabilities of Eqs.~\eqref{relprob}.
\begin{figure}[!t] 
\centering
\includegraphics[scale = 0.5]{distributioneng.pdf}
\caption{Probability distribution of spontaneous emissions for
  different number of cavity photons. Parameters $\mathcal{E}  =
  \kappa =  g = 1\gamma$, $100,000$ quantum trajectories. } \label{probdiss}
\end{figure}
If $\delta p > \epsilon$ is not fulfilled we just renormalize the
state, because using a non-hermitian Hamiltonian will have as a
consequence that the probability won't be conserved
\cite{Sakurai:1167961}. For the next step we repeat the procedure
using the resulting state for this step. One quantum trajectory of
total time $t$ is obtained after repeating the previous procedure
$t/\delta t$ steps. For each trajectory we count the number of quantum
jumps, the jumps corresponding to operator $a$ reduces the number of
photons inside the cavity and corresponds to a photon that leak the
cavity. The jumps corresponding to operator $\sigma_-$ interrumps its
unitary evolution and send it back to the ground state, it corresponds
to a spontaneous emission. The procedure to register emissions in the
two different channels is summarized in algorithm. \ref{alg1}.

@@

\section{Counting photons emitted in different channels}\label{sc:distributions}
In this section we calculate the probability distribution of the
number of spontaneous emissions $n_s$, under two different conditions.
First, we study the distribution probability of $n_s$ when we consider
the set of quantum trajectories where the number of leaked photons
from the cavity is $n_c$. This simulate the physical situation where
we count the number of spontaneous photons until the moment where the
number of leaked photons from the cavity is $n_c$. It is impossible to
know in advance how long it takes to the cavity to leak $n_c$ photons,
thus the duration of each quantum trajectory is not fixed. Second, we
fix the duration of each quantum trajectory and count the number of
spontaneous emissions $n_s$, and cavity emissions $n_c$. From the set
of quantum trajectories evolved a fixed time, we calculate the joint
probability $p(n_s,n_c)$, of finding $n_s$ spontaneous emissions and
$n_c$ cavity emissions. Using $p(n_s,n_c)$ we calculate the
conditional probability $p(n_s|n_c)$, and the correlations between the
two random variables. This correlation is a measure of how much
information we can obtain about $n_s$ if we know $n_c$.

@@

In order to find the value of the cavity drive $\mathcal{E}$ as a
function of the mean value of photons inside the cavity, we solve the
Maxwell-Bloch equations. These equations give the dynamic of our
system for the variables $\expval{a}, \expval{\sigma_-}$ and
$\expval{\sigma_z}$ that correspond to the cavity field, atomic
coherence, and atomic inversion respectively \cite{Alsing_1991}. In
our case, these equations are
\begin{subequations} \label{maxbloch}
\begin{equation} \label{bloch1}
\dot{z} = (g/2)v + \mathcal{E} - \kappa z,
\end{equation}
\begin{equation} \label{bloch2}
\dot{v} = gmz - (\gamma/2)v,
\end{equation}
\begin{equation} \label{bloch3}
\dot{m} = -2g(z^*v + v^*z) - \gamma(m + 2),
\end{equation}
\end{subequations} 
where we defined $z = e^{i\omega t}\expval{a}$,
$v = 2e^{i\omega t}\expval{\sigma_-}$ and $m = 2\expval{\sigma_z}$.
When the system is stable, we obtain, from
\eqref{maxbloch}, the steady state
solutions \cite{gagniuc2017markov}

@@

\subsection{Quantum trajectories with fixed number of photons leaked from the cavity}
We calculate the distribution probability of the number of spontaneous
emission when a fixed number of photons leaked the cavity. We assume
that the mean number of photons inside the cavity is $1/9$. The
results are shown in Fig.~\ref{probdiss}. As the number of cavity
emissions increases, the mean number of spontaneous emissions
increases. This result is expected, because the number of cavity
emissions is correlated with the time we are counting spontaneous
emission photons from the atom: the larger the number of cavity
emissions the larger the time we count spontaneous emitted photons,
which implies a larger mean number of emitted photons. Also, as shown
in Fig~\ref{graph}, the probability distribution is wider as the
number of leaked photons increases, this implies less accuracy
guessing the number of spontaneous emission. If we know the cavity
drive, this results does not imply that we can learn something extra
about the number of spontaneous emissions knowing the number of
photons leaked from the cavity; it is clear that when we increase the
time window where we count photons, both, the number of cavity emissions
and the number of spontaneous emissions, increases.

@@

\begin{figure}[!h]  
\centering
\includegraphics[scale = 0.5]{newsigma1.pdf}
\caption{Average number of spontaneous emissions with its standard
  deviation as a function of cavity emissions. Parameters: $\expval{n} \approx 1$, $\kappa = g = 0.1\gamma$}
\label{graph}
\end{figure}

\subsection{Quantum trajectories with fixed duration}
We consider the set of quantum trajectories of the same duration. This
corresponds to fixing the time we count photons. Each set of quantum
trajectories with the same duration is labeled with its mean number
of spontaneous emitted photons $\langle n_s\rangle$, given the system
parameters, a larger $\langle n_s\rangle$ implies quantum trajectories
with larger duration. We consider the case where we fix the mean
number of photons inside the cavity to $1$. As shown by
Eq.~(\ref{numfo}), this number depends on the drive, and cavity and
atomic parameters.

In Fig.~\ref{error2}(a) the probability distribution of spontaneous
emitted photons is shown for different duration of the quantum
trajectories. As it is shown in Fig.~\ref{error2}(b), the width of the
distribution increases linearly with the mean number of spontaneous
emissions. This behavior does not imply any correlation between the
number of spontaneous emissions and cavity emissions.

Now we focus in the case, where given a set of quantum trajectories
with fixed duration, we postselect all the trajectories where the
number of cavity emissions is a fixed number $n_c$, and plot
$p(n_s|n_c)$, the probability distribution of the number of spontaneous
emissions $n_s$, under the condition that $n_c$ cavity emissions
happened. If $p(n_s|n_c)\neq p(n_s)p(n_c)$, $n_s$ and $n_c$ are not
independent: information can be extracted about $n_s$ knowing $n_c$.
An example of this is shown in Fig.~\ref{probdisult}(a), where we
show $p(n_s|n_c)$, the probability distribution of $n_s$ postselected
to the case where the number of cavity emissions is
$n_c=\langle n_c \rangle$, and $n_c=\langle n_c \rangle\pm\sigma$. We
see a positive correlation between the two random variables: the
maximum of the probability distribution increases (decreases) if we
postselect the trajectories with a larger than the mean (smaller than
the mean) number of cavity emissions. In Fig.~\ref{probdisult}(b), we
show that for a cavity with large $\kappa$, the change in the
probability distribution $p(n_s|n_c)$ is much smaller than in the case
for small $\kappa$. When
$\kappa\rightarrow\infty$, there are no correlation between the two
channels and $p(n_s|n_c)=p(n_s)p(n_c)$.
In the next section we calculate the correlation between $n_s$ and
$n_c$ for different $\kappa$.

\begin{center}
\begin{figure*}[!t]
\includegraphics[scale = 0.5]{newerrorppp.pdf}
\caption{(a) Probability distributions for different mean number of
  spontaneous emissions $\langle n_s\rangle=\bar{n}_s$; (b)
  Variance of the random variable $n_s$ with respect to the mean number of
  spontaneous emissions. In both cases we consider
  $\expval{n} \approx 1$,  $\kappa = g = 0.1\gamma$.} \label{error2}
\end{figure*}
\end{center}

\begin{center}
\begin{figure*}
\begin{center}
\includegraphics[scale = 0.5]{lastgraph1.pdf}
\caption{Probability distribution of spontaneous emissions
  postselected to the condition that $n_c$ cavity emissions happened
  $p(n_s|n_c)$; observe, in both figures, the change in the
  probability distribution for spontaneous emissions for different
  postselections. (a) $\kappa = 0.05\gamma$,
  $\langle n_c\rangle=\bar{n}_c=50$, $\sigma=7$; (b) 
  $\kappa = 1.0$, $\langle n_c\rangle=\bar{n}_c=1000$, $\sigma=28$.
  Other parameters $\expval{n} \approx 1$, $g =0.1\gamma$,
  time of each trajectory: $500/\gamma$. } \label{probdisult}
\end{center}
\end{figure*}
\end{center}

\section{Correlation between photons emitted in different channels}\label{sc:correlation}
In this section we study the correlation between the number of
spontaneous emissions from the atom $n_s$, and the number of photons
that leak the cavity $n_c$, as a function of the cavity decay rate
$\kappa$. We expect that when $\kappa\rightarrow\infty$ there would be
no correlation between these two random variables, since this
situation is equivalent to the situation where there is no
cavity.

In order to calculate the correlation between emissions in the two
different channels, we use the Pearson correlation coefficient
\cite{benesty2009pearson}
\begin{equation} 
r_{n_s,n_c} = \frac{\sum\limits_{i=1}^n(n_s^{(i)} -
  \bar{n}_s)(n_c^{(i)} - \bar{n}_c)}{\sqrt{\sum\limits_{i=1}^n(n_s^{(i)}
    - \bar{n}_s)^2\sum\limits_{i=1}^n(n_c^{(i)} - \bar{n}_c)^2}}\, ,  \label{correlationc}
\end{equation}
where $n^{(i)}$ is the output $i$ of the random variable $n$.

\begin{center}
\begin{figure}[t!]
\begin{center}
\includegraphics[scale = 0.5]{million1.pdf}
\caption{Pearson correlation coefficient as a function of $\kappa$.
  The duration of the quantum trajectories is  $\gamma t_f = 500$.
  Other parameters $\expval{n} \approx 1$, $g = 0.1\gamma$.} \label{corrxy}
\end{center}  
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h!]
\begin{center}
\includegraphics[scale = 0.5]{million2.pdf}
\caption{Pearson correlation coefficient as a function of $\kappa$ for
  quantum trajectories with different duration. Parameters:
  $\expval{n} \approx 1$, $g = 0.1\gamma$.} \label{errorzz}
\end{center}
\end{figure}
\end{center}
%kncrease or increases

@@

The results are shown in Fig. \ref{corrxy}. We see a maximum
correlation close to $0.1$ for $\kappa/\gamma\approx 0.05$ that
decreases as $\kappa$ increases. The figure is consistent with the
statement that the correlation goes to zero as
$\kappa\rightarrow\infty$. With values for $\kappa/\gamma$ lower than
$0.05$, we notice that the correlations begins to decrease. The reason
is that, as the cavity linewidth decreases, the number of cavity
emissions decreases. In the limit where $\kappa=0$ the two random
variables becomes independent, because the output of $n_c$ is zero
with probability one. In this case there is no correlation between the
two random variables. Fig.~\ref{probdisult}(a), where the change in
$p(n_s|n_c)$ is larger, corresponds to a correlation around $0.1$;
Fig.~\ref{probdisult}(b), where the change is small, corresponds to a
correlation around $0.01$.
